---
title: "Mask Project Tables"
output: pdf_document
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(devtools)
```

```{r, echo=FALSE}
tab <- matrix(c(2,4,3,88,93,42,25,34,26),ncol=3)
colnames(tab) <- c("Floor", "Medical", "Non-Medical")
rownames(tab) <- c("Tues.", "Wed.","Thurs.")
```

<!----- This is table 1 code ----->
```{r, echo=FALSE}
knitr::kable(tab, 'simple', caption = "Frequency Distribution Table of People in The Library")
```

Simple table with the data aligned to the right.

<!----- This is table 2 code ----->
```{r, echo=FALSE}
knitr::kable(tab, "pipe", caption = "Frequency Distribution Table of People in The Library")
```

Pipe table otherwise same as the above.

<!----- This is table 3 code ----->
```{r, echo=FALSE}
knitr::kable(tab, "simple", align = 'ccc', caption = "Frequency Distribution Table of People in The Library")
```

Simple table with the data aligned to the right.

<!----- This is table 4 code ----->
```{r, echo=FALSE}
tab <- matrix(c("Tuesday", "Wednesday","Thursday", 2,4,3,88,93,42,25,34,26),ncol=4)
colnames(tab) <- c("Days", "Floor", "Medical", "Non-Medical")
knitr::kable(tab, "pipe", align = 'lccc', caption = "Frequency Distribution Table of People in The Library")
```
Labeling the days column and unabreviating the names.
\newpage
<!----- This is table 5 code ----->
```{r, echo=FALSE}
tab <- matrix(c("Tues.", "Wed.","Thurs.", 2,4,3,88,93,42,25,34,26),ncol=4)
colnames(tab) <- c("Days", "Floor", "Medical", "Non-Medical")
knitr::kable(tab, "pipe", align = 'lccc', caption = "Frequency Distribution Table of People in The Library")
```
Just labeling the days column.

<!----- This is table 6 code ----->
```{r, echo=FALSE}
tab <- matrix(c("Tuesday", "Wednesday","Thursday", 2,4,3,88,93,42,25,34,26),ncol=4)
colnames(tab) <- c("Days", "Floor", "Medical", "Non-Medical")
kbl(tab, format = "latex", align = 'lccc', caption = "Frequency Distribution Table of People in The Library") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```
Simple latex table.

<!----- This is table 7 code ----->
```{r, echo=FALSE}
kbl(tab, format = "latex", align = 'lccc', caption = "Frequency Distribution Table of People in The Library") %>%
  kable_styling(full_width = T, latex_options = c("striped", "hold_position"))
```
A full width table.

<!----- This is table 8 code ----->
```{r, echo=FALSE}
tab <- matrix(c("Tuesday", "Wednesday","Thursday", "Total", 2,4,3," ",88,93,42,223, 25,34,26,85, " "," "," ",308),ncol=5)
colnames(tab) <- c("Days", "Floor", "Medical", "Non-Medical","")
kbl(tab, format = "latex", align = 'lccc|c', booktabs = TRUE, caption = "Frequency Distribution Table of People in The Library") %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(1:3, extra_latex_after = "\\cline{1-5}") %>%
  sub("\\\\bottomrule", "", .)
```

This could be a way of displaying the sum of the frequencies.

<!----- This is table 9 code ----->
```{r, echo=FALSE}
tab <- matrix(c("Tuesday", "Wednesday","Thursday", "Total", 2,4,3," ",88,93,42,223, 25,34,26,85, 113,127,88,308),ncol=5)
colnames(tab) <- c("Days", "Floor", "Medical", "Non-Medical","Sums")
kbl(tab, format = "latex", align = 'lccc|c', booktabs = TRUE, caption = "Frequency Distribution Table of People in The Library") %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(3, extra_latex_after = "\\cline{1-5}")
```
This table includes sums of the rows and columns
\newpage

<!----- This is table 10 code ----->
```{r, echo=FALSE}
tab <- matrix(c("Tuesday", "Wednesday","Thursday","Total", '6 pm','5 pm','8 pm'," ", 2,4,3," ", 88,93,42,223, 25,34,26,85, 113,127,88,308),ncol=6)
colnames(tab) <- c("Days", "Times", "Floor", "Medical", "Non-Medical","Sum")
kbl(tab, format = "latex", align = 'lcccc|c', booktabs = TRUE, caption = "Frequency Distribution Table of People in The Library") %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(3, extra_latex_after = "\\cline{1-6}")
```

This table includes the times in which we recorded the data.






